---
title: "Vignette for the PeerGradedAssignmentPackage"
output: rmarkdown::html_vignette
author: "Marko Trifunovic"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Vignette for the PeerGradedAssignmentPackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PeerGradedAssignmentPackage)
```

# PeerGradedAssignmentPackage

This package contains a set of functions that should allow you to produce a
simple map of traffic accidents that occurred in the United States between
2013 and 2015. The mentioned functions will be listed below.


## The `make_filename` function

This function generates the filename string that will be used in
the `fars_read` function.

## The `fars_read` function

This function reads a single archive file based on the provided filename.

## The `fars_read_years` function

This function utilizes the `make_filename` function as well as the `fars_read`
function to import years in form of a list.

## The `fars_summarize_years` function
This function creates a summary data.frame of car accidents for given year(s).
Rows represent months, while different years are represented with columns.
For each month in a given year there is a number of accidents that were 
recorded.

## The `fars_map_state` function

This function generates a plot of accidents recorded across the selected state
during the given year.

# Dependencies

* dplyr
* readr
* magrittr
* rlang
* tidyr
* maps
* graphics
